---
title: "Linear regression models with package linearRegression"
author: "Teno González Dos Santos, Jose Luis López Ruiz, Enrique Josué Álvarez Robles"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Linear regression models with linreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette documents the content provided in the package linearRegression 1.0.0. This vignette is a high-level adjunct to the low-level details found in *?linearRegression*, *?linreg*, *?QRlinreg*, *?print.linreg*, *?plot.linreg* and *?summary.linreg*. You’ll learn how to work with linearRegression by creating a new object of class *linreg* with *QRlinreg()* and using methods such as *print()*, *plot()* or *summary()*.

## Creating an object of class linreg

### Class linreg

The key content in our package is the class linreg. This class is designed for dealing with linear regression models using QR decomposition method. It is organized the following way:

- **Attributes**

Attribute name | Description    
---------------|-----------------------------
coefficients   | vector of coefficients
predicted      | vector of predicted values
residuals      | vector of residuals  

- **Basic methods**

Method name  | Description    
-------------|-------------------------------------------
coef         | returns the vector of residuals e
pred         | returns the predicted values y
resid        | return the coefficients as a named vector  

### QRlinreg function

This function allows you to generate an object of class linreg given two parameters: a formula and a dataset. The parameter **formula** must be an R object of type *formula* and **data** must be a *data.frame*. The resulting object of class linreg will have stored all the statistics in it for the given parameters. In the following example you will see how to create this objects:

```{r QRlinreg, eval=FALSE}
data(iris)
linreg.obj <- QRlinreg(Sepal.Length ~ Sepal.Width, iris)
```

## Other useful methods of class linreg

In addition to the basic statistic methods that **linreg** provides, there are available other three different methods: *print()*, *plot()* and *summary()*. These methods override the conventional functions with identical name when an object of class *linreg* is passed as an argument.

### print() function

This is an *ad hoc* version of the ordinary *print()* function. It prints out the coefficients and coefficient names, similar as done by the *lm* class.

```{r print.linreg, eval=FALSE}
qr.obj <- QRlinreg(Sepal.Length ~ Sepal.Width, iris)
print(qr.obj)
```

### plot() function

This is an *ad hoc* version of the generic *plot()* function. It plots graphs using *ggplot2*.

```{r plot.linreg, eval=FALSE}
qr.obj <- QRlinreg(Sepal.Length ~ Sepal.Width, iris)
plot(qr.obj)
plot(qr.obj, standarized_residuals = TRUE)
```

### summary() function

This is an *ad hoc* version of the basic *summary()* function. It returns a similar printout as printed for *lm* objects, but only with the coefficients with their standard error, t-value and p-value as well as the estimate of *sigma* and the degrees of freedom in the model.

```{r summary.linreg, eval=FALSE}
qr.obj <- QRlinreg(Sepal.Length ~ Sepal.Width, iris)
summary(qr.obj)
```
